Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-16 Paper/Manuscript.tex
Updated plots

The normalised Hanning window, $\hannwnorm$, is given by: 
%
\begin{equation}
\label{eq:hannw}
\hannwnorm(\genidxsym) = \frac{\hannw(\genidxsym)}{\left( \frac{||\hannw||_2}{\sqrt{\nw}} \right)}, i = \frac{-\nw}{2}, \ldots, \frac{\nw}{2}
\end{equation}
%
and the discrete Fourier transform of the windowed data, $\ypcvolumef(\samplesymf)$, is then obtained from:
%
\begin{equation}
\label{eq:FFT_volume}
\ypcvolumef(\samplesymf) = \dft_\ndft 
\left( \hannwnorm(\genidxsym) \left(\ypcspread (\genidxsym+\samplesymt) \left[ u(\genidxsym + \frac{\nw}{2}) - u(\genidxsym - \frac{\nw}{2}) \right] \right) \right),
\end{equation}
%
where $u(\genidxsym)$ is the step function and $\samplesymt$ is the sample data index for the centre of the sliding window. The discrete Fourier transform of the auto correlation function of the matched filter signal, $\ymfautof(\samplesymf)$, also needs to be evaluated at the same frequencies:
%
\begin{equation}
\label{eq:FFT_TX_Auto}
\ymfautof(\samplesymf)  =  \dft_\ndft (\ymfauto(\samplesymt)).
\end{equation}
%
TODO: How to index samples along range? In the code \_n is used to indicate the range component of the FFt's. Needs attention.

@@

@@

>>>>

The normalised Hanning window, $\hannwnorm$, is given by: 
%
\begin{equation}
\label{eq:hannw}
\hannwnorm(\genidxsym) = \frac{\hannw(\genidxsym)}{\left( \frac{||\hannw||_2}{\sqrt{\nw}} \right)}, i = \frac{-\nw}{2}, \ldots, \frac{\nw}{2}
\end{equation}
%
and the discrete Fourier transform of the windowed data, $\ypcvolumef(\samplesymf)$, is then obtained from:
%
\begin{equation}
\label{eq:FFT_volume}
\ypcvolumef(\samplesymf) = \dft_\ndft 
\left( \hannwnorm(\genidxsym) \left(\ypcspread (\genidxsym+\samplesymt) \left[ u(\genidxsym + \frac{\nw}{2}) - u(\genidxsym - \frac{\nw}{2}) \right] \right) \right),
\end{equation}
%
where $u(\genidxsym)$ is the step function and $\samplesymt$ is the sample data index for the centre of the sliding window. The discrete Fourier transform of the auto correlation function of the matched filter signal, $\ymfautof(\samplesymf)$, also needs to be evaluated at the same frequencies:
%
\begin{equation}
\label{eq:FFT_TX_Auto}
\ymfautof(\samplesymf)  =  \dft_\ndft (\ymfauto(\samplesymt)).
\end{equation}

%
TODO: How to index samples along range? In the code \_n is used to indicate the range component of the FFt's. Needs attention.

@@

By rep pres of a set of centre samples n Sv values can be presented as a functon of range and frequencty for each ping
Teh range fo sentre samples n could be chosen to halv the window length or any other grid that the user prefer the data presented to be in. This can be usefull when combining the Sv(f) across a range of transducers. In thode our ex we have simply chosen n to be on the same order of the range resoluteion (fig.~\ref{Fig_Sv_m_n}).

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_m_n}
\caption{\label{Fig_Sv_m_n} Sv as a function of frequency ($m$) and range ($n$) for a single ping}
\end{figure}

For echo integration purposes it is common to integrate the Sv over a range, in our example we integrate the Sv from x-x m covering a school of non-swimbladdered fish (fig). We note that we normally require avg over several indivvidal pils to uptain an unbiased estimate of Sv for echo integration purposes. Here we present te sv(f) over the layer for our example ping for illustrative purposesn (fig.~\ref{Fig_Sv_m}).

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_m}
\caption{\label{Fig_Sv_m_n} Sv as a function of frequency ($m$) averaged over a range intervall covering a fish school }
\end{figure}

@@

In this implementation (ref code) several choices have been made. Some of these are well founded in signal processing literature whereas others are of a more practical and ad-hoc nature, where other approaches could been equally valid. These include, as examples,  
Transmit pulse
Tapering of the transmit pulse
Decimation factors and filters
When Convoling the recieved signal with the transmit pulse - edge cases
Assuemd four sector transducer
Matched load - hvor stor effekt å gå utover 
Assumed an impedance (trancuder)
Effective pulse duration...
Assuming SED algorithm, know the target depth. Improvements possible (SED for broadband). Number of samples for pulse comp - what is included, dense aggregations, sidelobes - pc, ...
Window siz
Edge cases - removed

...
